Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-09-30 WSSSPE3/report/wg_appendix_software_credit.tex
Reformatted group members to itemized list to ensure they appear in the right place.
Former-commit-id: e4584de998d67127bdd327661163fca316f83c01

\section{Software Credit Working Group Discussion}

\subsection{Group Members}
{\small
\begin{longtable}{ll}
   Alice Allen           &  Astrophysics Source Code Library (ASCL)
\\ Daniel S. Katz        &  University of Chicago \& Argonne National Laboratory
\end{longtable}
}

\subsection{Summary of Discussion}

\subsection{Description of Opportunity, Challenges, and Obstacles}

\subsection{Key Next Steps}

\subsection{Plan for Future Organization}

\subsection{What Else is Needed?}

\subsection{Key Milestones and Responsible Parties}

\subsection{Description of Funding Needed}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software Credit Working Group Discussion}
\label{sec:appendix_SW_credit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Kyle Niemeyer\footnote{email: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}} will serve as the point of contact for this working group, and be responsible for ensuring timely progress of the planned actions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Group Members}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item Alice Allen -- Astrophysics Source Code Library
\item Sou-Cheng Choi -- NORC at Univ.\ Chicago, Illinois Institute of Technology
\item James Hetherington -- University College London
\item Lorraine Hwang -- University of California, Davis
\item Daniel S.\ Katz -- University of Chicago \& Argonne National Laboratory
\item Frank Löffler -- Louisiana State University
\item Abby Cabunoc Mayes -- Mozilla Science Lab
\item Kyle E.\ Niemeyer -- Oregon State University
\item Grace Peng -- National Center for Atmospheric Research
\item Ilian Todorov -- Science \& Technology Facilities Council, UK
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Summary of Discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description of Opportunity, Challenges, and Obstacles}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Key Next Steps}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Plan for Future Organization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{What Else is Needed?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Key Milestones and Responsible Parties}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description of Funding Needed}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
